---
title: "THESIS"
author: "Jonathan R. Bacolod "
date: "Apr 03, 2019"
output:
    bookdown::word_document2:
      fig_caption: true
---

<!-- cd /host-rootfs/storage/emulated/0/GNURoot/home/R-Markdown/thesis/ -->

<!-- R -e 'rmarkdown::render_site(output_format = 'bookdown::word_document2', encoding = 'UTF-8')' -->

<!-- Rscript -e "rmarkdown::render('/host-rootfs/storage/emulated/0/GNURoot/home/R-Markdown/thesis/index.Rmd',  'all', encoding = 'UTF-8')" -->

<!-- Rscript -e 'bookdown::render_book("index.Rmd", "bookdown::word_document2")' -->

<!-- Rscript -e 'bookdown::render_book("index.Rmd", "bookdown::pdf_document2")' -->

nkw

<!--chapter:end:index.Rmd-->

---
title: "thesis"
output: 
  word_document:
    fig_caption: yes
    reference_docx: "thesis-format.docx"
  pdf_document: 
    fig_caption: yes
header-includes:
  \usepackage{placeins} 
  \usepackage{graphicx} 
  \usepackage{tikz} 
  \usetikzlibrary{arrows.meta}
  \usetikzlibrary{shapes.arrows}
  
---

<!-- Rscript -e "rmarkdown::render('/host-rootfs/storage/emulated/0/GNURoot/home/R-Markdown/thesis/hugot.Rmd',  'all')" -->

<!-- toc: true -->
<!-- bibliography: '/host-rootfs/storage/emulated/0/Documents/documents/latex/atan-thesis/hugot.bib' -->

<em>\FloatBarrier</em> 

##### <em>\newpage</em> 

# Chapter 1
```{r child = '/host-rootfs/storage/emulated/0/GNURoot/home/R-Markdown/thesis/chapters/chap1.Rmd'}
```
<em>\FloatBarrier</em> 

##### <em>\newpage</em> 
# Chapter 2
```{r child = '/host-rootfs/storage/emulated/0/GNURoot/home/R-Markdown/thesis/chapters/chap2.Rmd'}
```

<em>\FloatBarrier</em> 

##### <em>\newpage</em> 

```{r child = '/host-rootfs/storage/emulated/0/GNURoot/home/R-Markdown/thesis/chapters/chap3.Rmd'}
```

<em>\FloatBarrier</em> 

##### <em>\newpage</em> 


<!--chapter:end:hugot.Rmd-->

